Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-29 paper/paper.Rmd
clarify CLUTO clustering capabilities

Considering the wealth and continuing development of spatial and spatiotemporal partitioning techniques for specific applications, we will refrain from providing a complete account of these algorithms.
At present, \pkg{mlr3spatiotempcv} also supports spatiotemporal partitioning using the versatile CLUTO clustering algorithm [@cluto].
CLUTO is available in R through the \pkg{skmeans} package, which provides an interface to a downloadable compiled library with a restriction to non-commercial uses (see `?ResamplingSptCVCluto` in \pkg{mlr3spatiotempcv} for more information).

<!--- FIXME: It sounds like CLUTO can potentially be applied to spatial coordinates, space-time coordinates, or a combinations of coordinates and features. Does mlr3spatiotempcv support this, or is it limited to coordinates? If yes, perhaps this would be worth mentioning: "CLUTO can be used to partition data based on spatial coordinates, space--time coordinates, features, or a combination of these." -->

>>>>

Considering the wealth and continuing development of spatial and spatiotemporal partitioning techniques for specific applications, we will refrain from providing a complete account of these algorithms.
At present, \pkg{mlr3spatiotempcv} also supports spatiotemporal partitioning using the versatile CLUTO clustering algorithm [@cluto].
CLUTO is available in R through the \pkg{skmeans} package, which provides an interface to a downloadable compiled library with a restriction to non-commercial uses (see `?ResamplingSptCVCluto` in \pkg{mlr3spatiotempcv} for more information).
With respect to functionality, \pkg{mlr3spatiotempcv} supports two-dimensional clustering based on coordinates and three-dimensional clustering on coordinates and time.
Feature clustering is not supported.
